---
title: "Group Six, POLI 311 Project Code, all formulas weighed"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(foreign)
library(ggplot2)
library(lfe)
library(stargazer)
eu <- read.dta("ZA6963_v1-0-0.dta")
eudk <-read.dta("ZA6963_v1-0-0.dta")
```

# Outcome Variable = Support for the European Union (EU)'s Common Security and Defense Policy (CSDP)

```{r}
## This is our outcome variable in which we examine 
## support for the CSDP.
## We created a new dummy variale, in which "For" 
## was coded as 1 and "Against" coded as 0. 
##"Don't Know" (DK) and all other non-responses
## were coded out. 

eu <- filter(eu, qa16_4 %in% c("For", "Against")) 
eu <- eu %>%
  mutate(CSDP_opinion = ifelse(eu$qa16_4 == "For", 1, 0))

eu %>%
  ggplot(aes(x = CSDP_opinion)) +
  geom_bar() +
  ggtitle("Support for the CSDP") +
  xlab ("Positions: Against, For") +
  ylab ("Number of People")


## Acting on the Professor's advice, we did a 
## another version of the variable in which 
## DK responses were coded as 0, "For" was coded
## as 1 and "Against" was coded as -1.

eudk <- eudk %>% 
  mutate(CSDP_opinion= ifelse
         (eudk$qa16_4 == "For", 1, 
        ifelse(eudk$qa16_4 == "DK", 0, -1))) %>% 
  filter(!is.na(CSDP_opinion))

eudk %>%
  ggplot(aes(x = CSDP_opinion)) +
  geom_bar() +
  ggtitle("Support for the CSDP (with DK responses)") +
  xlab ("Positions: Againist, Don't Know and For") +
  ylab ("Number of people")
```

# Independent Variable = European Identity

```{r}
## This variable asked individuals to state their
## idenify on a scale goining from their nationality 
## only to european only. The variable was coded as 
## a dummy variable with individuals with any trace 
## of a european identify  coded as 1 and those only 
## idenifying with their nationality coded as 0. 
## All non-responses and other answers were coded out.

eu <- filter(eu, qd3 %in% c("(NATIONALITY) only",   
                            "(NATIONALITY) and European", 
                            "European and (NATIONALITY)",
                            "European only"))

eu <- eu %>%
  mutate(European_Identify = ifelse(eu$qd3 == "(NATIONALITY) and European" | 
                           eu$qd3 == "European and (NATIONALITY)" 
                           | 
                           eu$qd3 == "European only" , 
                           1, 0))

eu %>% 
  ggplot(aes(x = European_Identify)) +
  geom_bar() +
  ggtitle("European Identification") +
  xlab ("Positions: Nationality only, European") +
  ylab ("Number of people")

## A different version of the variable 
## with the respones: DK, no identify 
## and refusal to answer coded as 0. 
## Nationality only was coded as -1 
## and any trace of a European indentity 
## was coded as 1. 

eudk <- eudk %>% 
  mutate(European_Identify= ifelse(eudk$qd3 == "(NATIONALITY) and European" | 
                           eudk$qd3 == "European and (NATIONALITY)" | 
                           eudk$qd3 == "European only" , 1, ifelse(eudk$qd3 == "DK" |  
                          eudk$qd3 == "None (SPONTANEOUS)" | 
                          eudk$qd3 == "Refusal (SPONTANEOUS)", 0, -1 )))%>% 
 filter(!is.na(European_Identify))

eudk %>% 
  ggplot(aes(x = European_Identify)) +
  geom_bar() +
  ggtitle("European Identification (including DK responses)") +
  xlab ("Positions: Nationality, Don't Know, European ") +
  ylab ("Number of people")
```

# Confounding variable = Support for National Military

```{r}
## This variable asked individuals if they
## tended to trust or tended not to trust their 
## national military. The variable was coded as 
## a dummy variable with "tend to trust"coded 
## as 1 and "tend not to trust""  coded as 0. 
## DK and all other indecisive responses 
## were removed from the dataset.

eu <- filter (eu, qa8a_5 %in% c("Tend to trust", "Tend not to trust")) 
eu <- eu %>%
  mutate(Trust_national_military = ifelse(eu$qa8a_5 == "Tend to trust", 1, 0))

## A different version of the variable 
## with DK responses coded as 0. "Tend not 
## to trust" was coded as -1 and "tend 
## to trust"" was coded as 1. 

eudk <- eudk %>% 
  mutate(Trust_national_military= ifelse(eudk$qa8a_5 == "Tend to trust", 
                                 1, ifelse(eudk$qa8a_5 == "DK", 0, -1))) %>% 
  filter(!is.na(Trust_national_military))

```

# Confounding Variable = Direction of the EU

```{r}
## This variable asked individuals if they 
## felt the EU is going in the right direction. 
## "Things are going in the right direction" was 
## coded as 1, "Neither the one nor the other 
## (SPONTANEOUS)" was coded as 0 and "Things are
## going in the wrong direction" was coded as -1. 
## All other responses were coded out.

eu <- filter (eu, d73a_2 %in% c("Things are going in the right direction",   
                                  "Things are going in the wrong direction",
                                  "Neither the one nor the other (SPONTANEOUS)")
                                )
eu <- eu %>% 
  mutate(EU_right_direction= ifelse(eu$d73a_2== "Things are going in the right direction", 1,
                       ifelse(eu$d73a_2 == "Neither the one nor the other (SPONTANEOUS)", 
                              0, -1)))

## Same variable but with "DK"
## responses included, coded as 0.

eudk <- eudk %>% 
  mutate(EU_right_direction= 
           ifelse(eudk$d73a_2== "Things are going in the right direction", 1, 
          ifelse(eudk$d73a_2 == "Neither the one nor the other (SPONTANEOUS)" 
                 | eudk$d73a_2 ==  "DK", 0, -1))) %>% 
  filter(!is.na(EU_right_direction)) 
```

# Confounding Variable = Direction of the US

```{r}
## This variable asked individuals if they 
## felt the US is going in the right direction. 
## "Things are going in the right direction" was 
## coded as 1, "Neither the one nor the other 
## (SPONTANEOUS)" was coded as 0 and "Things 
## are going in the wrong direction" was coded as 
## -1. All other responses were coded out.

eu <- filter (eu, d73a_3 %in% c("Things are going in the right direction", 
                           "Things are going in the wrong direction",
                                  "Neither the one nor the other (SPONTANEOUS)")
                                )

eu <- eu %>% 
  mutate(US_right_direction= ifelse(eu$d73a_3 == "Things are going in the right direction", 1,
                       ifelse(eu$d73a_3 == "Neither the one nor the other (SPONTANEOUS)", 
                              0, -1)))

## Same variable but with "DK" respones
## included, coded as 0.

eudk <- eudk %>% 
  mutate(US_right_direction= 
           ifelse(eudk$d73a_3== "Things are going in the right direction", 1, 
        ifelse(eudk$d73a_3 == "Neither the one nor the other (SPONTANEOUS)" 
               | eudk$d73a_3 ==  "DK", 0, -1))) %>% 
  filter(!is.na(US_right_direction)) 
```

# Confounding Variable = Gender

```{r}
## This is the variable for gender. The only 
## responses which could be given were "Man" or "Woman".

eu %>% 
  ggplot(aes(x = d10)) +
  geom_bar() +
  ggtitle("Gender")

## Recoding the varible into a dummy variable, for 
## linear regression models with DK responses included.

eudk <- eudk %>% 
  mutate(Gender = ifelse(eudk$d10== "Woman", 0, 1))

## Recoding varible into a dummy variable, for 
## the linear regression models without DK respones.

eu <- eu %>% 
  mutate(Gender = ifelse(eu$d10== "Woman", 0, 1))
```

# Confounding Variable = Age

```{r}
## The variable for age, the range is from 
## 15 to 95.

eu %>% 
  ggplot(aes(x = d11)) +
  geom_bar() +
  ggtitle("Age")

## Assigning d11 to an object with a more 
## descriptive name, for linear regression 
## models with DK responses.

eudk <- eudk %>% 
  mutate(Age = eudk$d11)

## Assigning d11 to an object with a more 
## descriptive name, for linear regression 
## models without DK responses.

eu <- eu %>% 
  mutate(Age = eu$d11)
```

# Confounding Variable = Trust in the European Commission

```{r}
## This variable asked individuals if
## they tended to trust or tended not to 
## trust the European Commission, the
## European Union body responsible for 
## running the CSDP. The variable was coded 
## as a dummy variable with "tend to trust"
## coded as 1 and "tend not to trust" coded
## as 0. All other respones were coded out. 

eu <- filter(eu, qa14_2 %in% c("Tend to trust", "Tend not to trust"))
eu <- eu %>%
  mutate(Trust_EU_Commission = ifelse(eu$qa14_2 == "Tend to trust", 1, 0))

## The same variable, but with DK responses
## included, coded as 0. "Tend to trust"
## coded as 1, and "tend not to trust"
## coded as -1.

eudk <- eudk %>% 
  mutate(Trust_EU_Commission= 
           ifelse(eudk$qa14_2 == "Tend to trust", 1,    ifelse(eudk$qa14_2 == "DK", 0, -1))) %>% 
  filter(!is.na(Trust_EU_Commission)) 
```

# Confounding Variable = Financial Situation in the Household

```{r}
## This variable asked individuals about 
## their opinion of the state of their 
## household's finacial situation. The variable 
## was recoded into a dummy variable with 
## "very good" and "rather good" being coded 
## as 1 and "rather bad" and "very bad" being 
## coded as 0. All other responses were coded out.

eu <- filter(eu, qa1a_5 %in% c("Very good", "Rather good", "Rather bad","Very bad"))

eu <- eu %>% 
  mutate(Financial_situation= ifelse(eu$qa1a_5== " Very good" | 
                              eu$qa1a_5== "Rather good", 1, 0))

## The Same variable but with DK reponses 
## included, coded as 0."Rather bad" and
##  "very bad" coded as -1 and "rather good"
##  and "very good" coded as 1.

eudk <- eudk %>% 
  mutate(Financial_situation= 
           ifelse(eudk$qa1a_5== " Very good" | 
                  eudk$qa1a_5== "Rather good", 1, 
                  ifelse(eudk$qa1a_5 == "DK", 0, -1))) %>% 
  filter(!is.na(Financial_situation)) 

```

#Weighting Variable

```{r}
## The Professor advised us during the poster
## session, that the Eurobarometer survey has
## weight variables and we should include them
## in our linear regression models. The Variable 
## w23 weighs for the differences between the 28 
## nations of the EU. As it was the most encompassing 
## weight variable, that is why it was selected.

## Assigning w23 to an object with a more 
## descriptive name, for linear regression 
## models with DK responses.

eudk <- eudk %>% 
  mutate(weight =eudk$w23)

## Assigning w23 to an object with a more 
## descriptive name, for linear regression 
## models without DK responses.

eu <- eu %>% 
  mutate(weight =eu$w23)
```

#Fixed Effects, controlling for country of orgin

```{r}
## We decided to control for the fixed 
## effects of country of orgin. However, 
## the Eurobarometer survey coded West 
## and East Germany as well as Great Britain 
## and Northern Ireland separatly. We decided to 
## re-combine the two pairs to reflect the 
## geo-political realities of the present.

eu$iso <- eu$isocntry
eudk$iso <-eudk$isocntry

## Re-combining West and East Germany for the
## dataset with DK responses coded out.

eu$iso[eu$iso %in% c("DE-E", "DE-W")] <- "DE"

## Re-combining Great Britain and Northern Ireland
## for the dataset with DK responses coded out.

eu$iso[eu$iso %in% c("GB-GBN", "GB-NIR")] <- "GB"

## Repeating the process for the dataset with DK 
## responses included.


eudk$iso[eudk$iso %in% c("DE-E", "DE-W")] <- "DE"
eudk$iso[eudk$iso %in% c("GB-GBN", "GB-NIR")] <- "GB"
```

# Linear regression models 
# for the variables which 
# include DK responses

```{r}
## DK, Model 1: support for the CSDP and  
## European identify. 

dkm1 <-lm(CSDP_opinion ~ European_Identify, 
          data = eudk, 
          weigh = eudk$weight)
summary(dkm1)

## DK, Model 2: same as model 1 but 
## controling for support for national 
## military and the EU Commission. 

dkm2 <-lm(CSDP_opinion ~ European_Identify 
          + Trust_national_military 
          + Trust_EU_Commission, 
          data = eudk, 
          weigh = eudk$weight)
summary(dkm2)

## DK, Model 2f: model 2 but applying 
## fixed effects, controlling for 
## country of orgin. 

dkm2f <- felm(CSDP_opinion ~ European_Identify         
              + Trust_national_military 
              + Trust_EU_Commission
              |  
              eudk$iso, 
              data = eudk,
              weigh = eudk$weight)
summary(dkm2f)

## DK, Model 3: same as model 2 but 
## adding the variables for EU/US direction.

dkm3 <- lm(CSDP_opinion~ European_Identify + 
              Trust_national_military + 
              Trust_EU_Commission +
              EU_right_direction +
              US_right_direction 
              , data = eudk,
           weigh = eudk$weight)
summary(dkm3)

## DK, Model 3f: same model as Model 3 but 
## applying fixed effects, controlling for 
## country of orgin. 

dkm3f <- felm(CSDP_opinion ~ European_Identify + 
                      Trust_national_military + 
                      Trust_EU_Commission + 
                      EU_right_direction +  
                      US_right_direction
                       |
                      eudk$iso,
                      data = eudk,
                      weigh = eudk$weight)
summary(dkm3f)

## DK, Model 4: same as model 3 but controlling for  
## the demographic variables. 

dkm4 <- lm(CSDP_opinion ~ European_Identify + 
               Trust_national_military +
               Trust_EU_Commission + 
               EU_right_direction +
               US_right_direction + 
               Financial_situation + 
               Age + 
               Gender, 
              data = eudk, 
              weigh = eudk$weight)
summary(dkm4)

## DK, Model 4f: same model as Model 4 
## but applying fixed effects, controlling 
## for country of orgin. 

dkm4f <- felm(CSDP_opinion ~ 
                European_Identify + 
                Trust_national_military + 
                Trust_EU_Commission + 
                EU_right_direction + 
                US_right_direction + 
                Financial_situation + 
                Age 
                + Gender
               |eudk$iso,
                 data = eudk,
              weigh = eudk$weight)
summary(dkm4f)
```

#Tables of the Linear Regression models 
#using variables that include DK responses, 
#using Stargazer

```{r, results = "asis"}
## Table of Linear Regression models including
## Don't Know responses

stargazer (title = "Weighted Linear Regression models of 
           support for the EU's CSDP (including 
           Don't Know responses)",
           dkm1, dkm2, dkm3, dkm4,
           column.labels = c("dkm1", "dkm2", 
                             "dkm3", "dkm4"),
           column.sep.width = "-20pt",
           font.size = "small",
           header = FALSE)

## Table of Linear Regression models that
## control for fixed effects, including 
## Don't Know responses.
  
stargazer(title = "Weighted Linear Regression models 
          with Fixed effects, of 
          support for the EU's CSDP
          (including Don't Know responses)",
          dkm2f, dkm3f, dkm4f, 
          column.labels = c("dkm2f", 
                            "dkm3f", "dkm4f"),
          column.sep.width = "-20pt",
          font.size = "small",
          header = FALSE)
```

## Linear regression models for variables
## with DK responses removed 

```{r}
# Model 1: support for the CSDP and European identify. 

m1 <-lm(CSDP_opinion ~ European_Identify, data = eu, weigh = eu$weight)
summary(m1)

## Model 2: same as model 1 but controling for
## support for national military and the EU Commission. 

m2 <-lm(CSDP_opinion ~ European_Identify 
                    + Trust_national_military 
                    + Trust_EU_Commission, 
                    data = eu, weigh = eu$weight)
summary(m2)

##  Model 2f: model 2 but applying 
##  fixed effects, controlling for 
## country of orgin . 

m2f <- felm(CSDP_opinion ~ European_Identify 
                 + Trust_national_military 
                 + Trust_EU_Commission
                 | 
                 eu$iso , 
                 data = eu,
                 weigh = eu$weight)
summary(m2f)

## Model 3: same as model 2 but adding the 
## variables for EU/US directions.

m3 <- lm(CSDP_opinion ~ European_Identify + 
              Trust_national_military + 
              Trust_EU_Commission +
              EU_right_direction +
              US_right_direction 
              , data = eu, weigh = eu$weight)
summary(m3)

## Model 3f: same as model 3 but applying 
## fixed effects, controlling for country 
## of orgin. 

m3f <- felm(CSDP_opinion ~ European_Identify + 
                      Trust_national_military + 
                      Trust_EU_Commission + 
                      EU_right_direction +  
                      US_right_direction
                      |
                      eu$iso, 
                      data = eu,
                      weigh = eu$weight)
summary(m3f)

## Model 4: same as model 3 but controlling for 
## the demographic variables. 

m4 <- lm(CSDP_opinion ~ European_Identify + 
               Trust_national_military +
               Trust_EU_Commission + 
               EU_right_direction +
               US_right_direction + 
               Financial_situation + 
               Age + 
               Gender, 
               data = eu, 
              weigh = eu$weight)
summary(m4)

## Model 4f: same model as Model 4 but 
## applying fixed effects, controlling 
## for country of orgin. 

m4f <- felm(CSDP_opinion ~ 
                European_Identify + 
                Trust_national_military +
                Trust_EU_Commission + 
                EU_right_direction +
                US_right_direction + 
                Financial_situation + 
                Age + 
                Gender
                |eu$iso,
                data = eu,
                weigh = eu$weight)
summary(m4f)
```

## Tables of the Linear Regression models,
## of variables without Don't Know responses, 
## using Stargazer

```{r, results = "asis"}
## Table of Linear Regression models without 
## Don't Know responses

stargazer (title = "Weighted Linear Regression models 
           of support for the EU's CSDP (without Don't Know responses)",
           m1, m2, m3, m4, 
           column.labels = c("m1", "m2", "m3", "m4"),
           column.sep.width = "-20pt",
           font.size = "small",
           header = FALSE)

## Table of Linear Regression models 
## controlling for Fixed effects, without Dk.

stargazer(title = "Weighted Linear Regression models 
          with fixed effects, of support for 
          the EU's CSDP (without Don't Know responses",
          m2f, m3f, m4f, 
          column.labels = c("m2f", "m3f", "m4f"),
          column.sep.width = "-20pt",
          font.size = "small",
          header = FALSE)
```




## Equations for the linear regression 
## models, done in LaTeX


$$CommonEuropeanDefence_i = 
\alpha_{EuropeanIdentity} + \epsilon$$



$$CommonEuropeanDefence = 
\alpha_{1_EuropeanIdentity} + 
\beta_{1_SupportForNationalMilitary} +
\beta_{2_SupportForTheEC}$$


$$+\beta_{3_DirectionOfTheUSA} + 
\beta_{4_DirectionOfTheEU} + 
\beta_{5_FinancialSituation} + 
\beta_{6_Age} + 
\beta_{7_Gender}$$

$$+\epsilon, ControlledforCountryofOrigin $$

$$CommonEuropeanDefence = 
\alpha_{1 EuropeanIdentity} + 
\beta_{1 SupportForNationalMilitary}$$

$$+\beta_{2 SupportForTheEC} + 
\beta_{3 DirectionOfTheUSA} + 
\beta_{4 DirectionOfTheEU}$$


$$+ \beta_{5 FinancialSituation} + 
\beta_{6 Age} + 
\beta_{7 Gender} + 
\epsilon, FixedEffects$$ 

